Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-11 article.tex
add tabs + values for inverse correlation (roc)

\begin{table}[htb]
\centering
\caption{Improvement of each stage of our approach Note that we choose the
         \textit{best} threshold for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Inverse correlation & & & & \\
Pre-processing      & & & & \\
PCA                 & & & & \\
Weighting           & & & & \\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Comparison with other methods}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation         & & & & \\
Partial correlation & & & & \\
Our approach        & & & & \\
GENIE3              & & & & \\
GTE                 & & & & \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[htb]
\centering
\caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
P-A                 & 0.925 & 0.925 & 0.924 & 0.923 \\
P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & & & & \\
PCA                 & & & & \\
Weights             & & & & \\
Weights + PCA       & & & & \\
H-T                 & & & & \\
H-T + PCA           & & & & \\
H-T + Weights       & & & & \\
H-T + Weights + PCA & & & & \\
PCA                 & & & & \\
P-P + PCA           & & & & \\
P-P + Weights       & & & & \\
P-P + Weights + PCA & & & & \\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Correlation. Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.681 (0.028) & & & \\
hard-threshold      & 0.876 (0.143) & & & \\
Pre-processing      & 0.857 (0.100) & & & \\
PCA                 & & & & \\
Weighting           & 0.826 (0.079) & & & \\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Comparison with other methods (for now, $t = 0.11$)}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation         & & & & \\
Partial correlation & & & & \\
Our approach        & & & & \\
GENIE3              & & & & \\
GTE                 & & & & \\
\bottomrule
\end{tabular}
\end{table}
